An Answer Set Programming Framework for Reasoning about Agents' Beliefs and Truthfulness of Statements

### 2020-06-18 main.tex
Related work on trust and AI expanded.

The AI community has explored the issue of computational trust and reputation in several works---please see \cite{SabaterS05} for a survey. The survey focuses predominantly on trust models observed in multi-agent scenarios, taking explicitly into account the observations concerning interactions among agents. The survey provides classification of the models according to different dimensions: conceptual model (cognitive vs. game theoretical), information sources (direct interactions, direct observations, witness information, sociological information, prejudice), visibility (subjective vs. global), granularity (context dependent vs. non-context dependent), model type (trust vs. reputation), type of information exchanged (boolean vs. continuous), and agent behavior's assumptions (honest, biased but not lying, lying). Within such classification, our model focuses on trust---but could easily accommodate other interesting forms of reputation)---based on cognitive aspects, it builds on direct observations, but can accommodate sociological biases and prejudice through defaults, it captures subjective visibility, it is context dependent and relies on boolean information.

>>>>

The AI community has explored the issue of computational trust and reputation in several works. It should be noted that the term ``trust'' is associated with many orthogonal directions of research. For instance, some researchers intend trust as a measure of the probability that an agent will complete a given task \cite{pg19}. Others evaluate have studied how trust can be measured in terms of opinions based on, e.g., user ratings or feedback \cite{dbq20}. Others still have developed techniques for reasoning while taking into account information about trust (of agents, of statements, etc.) \cite{tcm12}.

Views of trust closer to ours can be found, e.g., in \cite{SabaterS05} for a survey. The survey focuses predominantly on trust models observed in multi-agent scenarios, taking explicitly into account the observations concerning interactions among agents. The survey provides classification of the models according to different dimensions: conceptual model (cognitive vs. game theoretical), information sources (direct interactions, direct observations, witness information, sociological information, prejudice), visibility (subjective vs. global), granularity (context dependent vs. non-context dependent), model type (trust vs. reputation), type of information exchanged (boolean vs. continuous), and agent behavior's assumptions (honest, biased but not lying, lying). Within such classification, our model focuses on trust---but could easily accommodate other interesting forms of reputation)---based on cognitive aspects, it builds on direct observations, but can accommodate sociological biases and prejudice through defaults, it captures subjective visibility, it is context dependent and relies on boolean information.
